---
title       : Names Application
subtitle    : How Popular is your name ??
author      : Sebastian Laborde
job         : 
framework   : revealjs      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default       # 
widgets     : [nvd3]            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3,libraries/morris,libraries/polycharts]}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## Names Application

<span style="color:green; font-weight:bold">Objective:</span>
Answer the question How Popular is your name between 1960 and 2010 ??

## It is easy to use and very funny.

--- .class #id 

## How to use it ??

## The Input:
### You only provide your name and your birth year.


--- .class #id 

## How to use it ??

## The Ouput:

1. **You get the total people (with the name you entered) born in the year you input.** 
2. **In the first tab you get an interactive line chart using NVD3 with the statistics of the name you entered.**
3. **In the second tab you get a donut chart wiht the top 10 popular male names in the year you entered.**
4. **In the third tab you get a donut chart wiht the top 10 popular female names in the year you entered.**

--- .class #id 

## Example

## Line Chart on 3rd Tab for Sebastian


```{r, echo=FALSE, warning=FALSE}
userData <- function(names){
      userData <- subset(data, Name == names)
}

top10 <- function(year, gender){
      top10 <- subset(data, Year == year & Sex == gender, select = c('Name','TotalBirth'))
      top10 <- top10[order(-top10$TotalBirth),]
      head(top10, 10)
}

colClasses <- c('numeric','factor','factor', 'character')
data <- read.csv('nombre_nacim_por_anio_y_sexo.csv', 
                 header = TRUE, na.strings = "NA", colClasses = colClasses,  skipNul = TRUE)

data <- subset(data, Name != '') 
data <- data.frame(Year = data$Year, Sex = data$Sex, Name = data$Name, 
                   TotalBirth = as.numeric(data$TotalBirth))

uData <- userData('SEBASTIAN')
if (nrow(uData) > 0) {
      uData <- aggregate(data = uData, TotalBirth ~ Year + Name, sum) 
      x <- subset(uData, Year == 1979, select = c('Year','TotalBirth'))
}
```

```{r nvd3plot, results = 'asis', comment = NA, message = F, echo = F}
library(ggplot2)
library(devtools)
library(rCharts)
library(knitr)

n1 <- nPlot(TotalBirth ~ Year, data = uData, group = 'Name', 
                              type = "lineChart")
n1$addParams(dom = 'stat', width = 600, height = 300)
n1$show(cdn = TRUE)
```




#### Check it at [shinyapps](https://slaborde.shinyapps.io/workspace/)



